---
title: "Problem sequence analyses"
output: html_notebook
---


```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
```


```{r}
input_shareds = c("False")#, "True")
tasks = c("XOR_of_XORs", "XOR", "AND", "OR")
lrs = c(0.005, 0.00125)
nhs = c(80, 20)
ims = c(1., 0.33)
num_runs = 100
num_epochs = 20000
directory_format = "sequence_results_nh_%i_lr_%.4f_im_%.2f/"

d = data.frame()
for (run in 0:(num_runs-1)) {
  for (input_shared in input_shareds) {
    for (num_hidden in nhs) {
      for (lr in lrs) {
        for (init_mult in ims) {
          directory = sprintf(directory_format, num_hidden, lr, init_mult)
          for (task in tasks) {
            filename = sprintf("%stask%s_sharedinput%s_run%i.csv", directory, task, input_shared, run)
            if (!file.exists(filename)) {
              next
            }
            this_d = tryCatch(read.csv(filename, header=T),
                              error = function(cond) {return(NA)})
            if (length(this_d) == 1 && is.na(this_d)) {
              next
            }
            this_d$num_hidden = num_hidden
            this_d$lr = lr
            this_d$init_size = init_mult
            this_d$run = run
            this_d$task = task
            this_d$input_shared = input_shared
            d = bind_rows(d, this_d)

          } 
        }
      }
    }
  }
}
```

```{r}
d = d %>%
  gather(loss_index, loss, contains("loss")) %>%
  mutate(task_repeat = epoch %/% num_epochs,
         epoch = epoch %% num_epochs,
         loss_index = substring(loss_index, 5)) %>% 
  filter(loss_index == task_repeat) %>% # only keep the loss for the current task
  select(-loss_index)
  
```

```{r}
success_d = d %>%
  group_by(num_hidden, lr, init_size, input_shared, task, run, task_repeat) %>%
  summarize(successful = any(loss < 0.05)) %>%
  ungroup() %>%
  group_by(num_hidden, lr, init_size, input_shared, task, task_repeat) %>%
  summarize(pct_successful = sum(successful)/n()) %>%
  ungroup()
```

```{r}
theme_set(theme_bw())
```

```{r}
ggplot(success_d, aes(x=task_repeat, y=pct_successful, color=task)) +
  geom_point() +
  geom_line() +
  scale_color_brewer(palette="Dark2")+
  facet_grid(num_hidden + init_size ~ lr)
ggsave("plots/sequences/success_results.png")
```

```{r}
time_d = d %>%
  filter( loss < 0.05) %>%
  group_by(num_hidden, lr, init_size, input_shared, task, run, task_repeat) %>%
  summarize(success_time = min(epoch)) %>%
  ungroup() %>%
  group_by(num_hidden, lr, init_size, input_shared, task, task_repeat) %>%
  summarize(se_st = sd(success_time)/sqrt(n()),
            success_time = mean(success_time),
            st_lo = success_time - 1.96 * se_st,
            st_hi = success_time + 1.96 * se_st) %>%
  ungroup()
```


```{r}
ggplot(time_d, aes(x=task_repeat, y=success_time, color=task)) +
  geom_point() +
  geom_errorbar(aes(ymin=st_lo, ymax=st_hi), width=0.25) +
  geom_line() +
  scale_color_brewer(palette="Dark2")+
  facet_grid(num_hidden + init_size ~ lr, scales="free_y")
ggsave("plots/sequences/success_time_results.png")
```

```{r}
ggplot(time_d %>% filter(task %in% c("XOR")), aes(x=task_repeat, y=success_time, color=task)) +
  geom_point() +
  geom_errorbar(aes(ymin=st_lo, ymax=st_hi), width=0.25) +
  geom_line() +
  scale_color_brewer(palette="Dark2", drop=F)+
  facet_grid(num_hidden + init_size ~ lr, scales="free_y")
ggsave("plots/sequences/success_time_results_XOR.png")
```
Evidence of transfer for more complicated tasks (generally continuing to improve with repeats, especially when weights are small). In some cases (20 hidden, init_mult 0.33) even if initial learning is not successful it will benefit transfer(!).


```{r}
ggplot(time_d %>% filter(task %in% c("AND", "OR")), aes(x=task_repeat, y=success_time, color=task)) +
  geom_point() +
  geom_line() +
  scale_color_brewer(palette="Dark2")+
  facet_grid(num_hidden + init_size ~ lr, scales="free_y")
ggsave("plots/sequences/success_time_results_easy.png")
```

By contrast, simpler tasks seem to show more negative transfer, especially AND (although learning is very fast so this may just be a capacity issue, maybe trying adding hidden units each time instead of giving them all from the beginning?)